\gle{acd}{ACD}{Affected Class Diagram}{Class diagram containing classes affected by changes between two versions of the same program. Based on identifying modified and deleted methods.}

\gle{aop}{AOP}{Aspect-oriented Programming}{Programming paradigm aiming to increase modularity by allowing cross-cutting concerns, that is, aspects of programs affecting other concerns. An example of a cross-cutting concern is logging because a logging strategy affects every logged part of a system.}

\gle{api}{API}{Application Programming Interface}{Specification on how software components should interact with each other. This can, for example, be to access databases or hardware, like hard disk drives or graphic cards. Usually exposes specifications, data structures, classes, and available requests.}

\gle{ci}{CI}{Continuous Integration}{The software engineering practice of continuously integrating development changes into a shared version control system, and with that integration, build, run, and test the integrated system.}

\gle{cig}{CIG}{C\# Interclass Graph}{Representation of the control flow between different methods in the affected classes. Graph generation is based on the \gls{acd}.}

\gle{cil}{CIL}{Common Intermediate Language}{The lowest level human-readable programming language defined in the \gls{cli} and used in the .NET framework. Languages intended to be compatible with the \gls{cli} compile source code into this format.}

\gle{cli}{CLI}{Common Language Infrastructure}{An open Microsoft specification describing executable code and a runtime environment allowing the use of multiple high-level languages on various computer platforms and architectures.}

\gle{clr}{CLR}{Common Language Runtime}{The virtual machine of the Microsoft .NET framework, responsible for executing .NET programs. The component handles memory, type safety, exceptions, garbage collection, and thread management. Compilation is done by the \gls{jitter}.}

\gle{fep}{FEP}{Fault-Exposing-Potential}{The chance that a fault in a branch or program statement, covered by a test case, will actually cause a failure for the test case. Practical determinations of this measure are approximations.}

\gle{ide}{IDE}{Integrated Development Environment}{Software application providing assisting facilities to software developers. Typically consists of a source code editor with code completion and build automation tools with a debugger, along with several other components aiding development.}

\gle{ieee}{IEEE}{Institute of Electrical and Electronics Engineers}{Professional association dedicated to advancing technological innovation and excellence. Includes 38 societies organized around specialized fields, with over 300 local organizations.}

\gle{iis}{IIS}{Internet Information Services}{A web server created by Microsoft for use with the Windows operating systems. IIS Express is a lightweight, standalone, freeware alternative.}

\gle{il}{IL}{Intermediate Language}{An intermediate language between source code and machine code, usually referring to \gls{cil} code.}

\gle{jit}{JIT}{Just-In-Time}{Refers to just-in-time compilation, where the compilation is performed as the program executes, rather than before. Just-in-time compilation usually compiles from a given format into machine code, which can then be executed by the running machine.}

\gle{jitter}{JITTER}{Just-In-Time Compiler}{Sometimes also spelled \textit{JITter} and refers to a compiler using a \gls{jit} compilation strategy, where code is compiled as the program executes.}

\gle{json}{JSON}{JavaScript Object Notation}{An open standard format derived from the JavaScript programming language. The format uses human-readable text to store data objects as key-value pairs, where the key is an attribute name.}

\gle{pie}{PIE}{Propagation, Infection, and Execution}{Model used as foundation for regression testing techniques. The model states that a fault can be detected by a test if a faulty statement is executed and infects the state, so that an error propagates to an observable output.}

\gle{rto}{RTO}{Regression Test Suite Optimization}{NP-Complete optimization problem of optimizing a test suite. Covers all types of regression testing techniques. Single-objective techniques optimizes a test suite in one regard; multi-objective in several.}

\gle{spin}{SPIN}{Software Process Improvement Network}{Independent organization with professional interested in the improvement of software and systems processes.}

\gle{sql}{SQL}{Structured Query Language}{Programming language with the purpose of managing data in a relational database management system. The programming language is based on relational algebra and tuple relational calculus. Consists of a data definition language and a data manipulation language.}

\gle{sut}{SUT}{System Under Test}{Term used in software testing to denote a system that is being tested for correctness, according to some set of system specifications.}

\gle{tdd}{TDD}{Test-Driven Development}{Agile software development strategy where automated tests are written prior to the development of functional code. Tests are used to drive design and programming.}

\gle{uml}{UML}{Unified Modeling Language}{General-purpose modeling language which provides a standardized way of visualizing the design and architecture of a system.}

\gle{xp}{XP}{Extreme Programming}{Agile software development methodology for improving software quality and responsiveness to customer requirements. Frequent releases, pair programming, and extensive code review are example concepts.}